Report: Complex Support Vector Detector for Large MIMO System

### 2015-10-20 Report Aug 5 2015/Report Aug 2015.tex
simulation matlab code

  We first introduce 1-D work set selection strategy in which single optimization variable whose update can maximize the gain of the sub dual objective function is chosen as the work set in each iteration. Define $\Lambda=[\lambda_{1}, \lambda_{2}, \ldots, \lambda_{N_{r}}]^{T}$, $\sigma_{i}=\lambda_{i}^{new}-\lambda_{i}$, $\Sigma=[\sigma_{1}, \sigma_{2}, \ldots, \sigma_{N_{r}}]^{T}$. Substitute $\mathbf{a}, \hat{\mathbf{a}}$ with $\Lambda$ and using $\Sigma$. Let $\Lambda_{S}$ and $\Sigma_{S}$ denote the vector that consist of the components in $\Lambda$ and $\Sigma$ that belong to work set $S$, the sub dual objective function in (\ref{subset optimization}) and its gain (\ref{gain work set selection2}) can be rewritten as 
  \begin{equation}
\max_{\Lambda_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[\Lambda_{S}^{T}\Re{(\mathbf{K})}_{SS}\Lambda_{S}]+[\Re{(\mathbf{y}_{S}^{T})}-\Lambda_{N}^{T}\Re{(\mathbf{K})}_{NS}
]\Lambda_{S}-\epsilon<\mathbf{e}_{S}^{T}, |\Lambda_{S}|>,
\label{subset optimization lambda}
\end{equation}

\begin{IEEEeqnarray}[\relax]{l}
\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}\Sigma^{T}_{S}\Re{(\mathbf{K})}_{SS}\Sigma_{S}+(\Phi^{r}_{S})^{T}\Sigma_{S}-\epsilon<\mathbf{e}^{T}_{S},|\Lambda^{new}_{S}|-|\Lambda_{S}|>,
\label{gain work set selection lambda}
\end{IEEEeqnarray} 
In 1-D solver, $|S|=1$, based on (\ref{gain work set selection lambda}), the sub dual objective function corresponding to the $m$th optimization variable $\tilde{\lambda}^{new}_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
\begin{IEEEeqnarray}[\relax]{l}
 \max_{\tilde{\lambda}^{new}_{m}}\quad \theta_{m}^{r}=-\frac{1}{2}(\tilde{\lambda}_{m}^{new})^{2}\Re{(\mathbf{K})}_{mm}
+[\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\Re{(\mathbf{K})}_{mj}\lambda_{j}]\tilde{\lambda}_{m}^{new}-\epsilon(|\tilde{\lambda}^{new}_{m}|),
 \label{optimization function 1-D}
 \end{IEEEeqnarray}
 where $\tilde{\lambda}^{new}_{m}$ is the update of $\lambda_{m}$.
 Based on the definition of $\Phi$ in (\ref{gain work set selection2}), $\Phi^{r}_{i}=\Re{(\mathbf{y}_{i})}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re{(\mathbf{K})}_{ij}$, similarly, as to dual variable $\lambda^{i}_{i}$ in the imaginary channel, $\Phi_{i}^{i}=\Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}$. Thereafter, for sake of brevity, we use $\lambda_{i}$ instead of $\lambda_{i}^{r}$.
Take the partial derivative of $\theta_{m}^{r}$ respect to $\tilde{\lambda}^{new}_{m}$,  we have 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\frac{\partial \theta_{m}^{r}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))
\label{partial optimization function 1-D lambda}
\end{IEEEeqnarray} 
where $\Re(y_{m})-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re(\mathbf{K})_{mj}=\Re(y_{m})-\sum_{j=1}^{N_{r}}\lambda_{j}\Re(\mathbf{K}_{mj})=\Phi^{r}_{m}+\lambda_{m}\Re(\mathbf{K}_{mm})$
and $\lambda_{m}$ denotes the $m$th optimization variable before update. Therefore (\ref{partial optimization function 1-D lambda}) can be rewritten as 
\begin{IEEEeqnarray}[\relax]{l}
\frac{\partial \theta^{r}_{m}}{\partial \tilde{\lambda}_{m}^{new}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}+\lambda_{m}\Re{(\mathbf{K})}_{mm}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))\\
\Rightarrow \tilde{\lambda}_{m}^{new}=\lambda_{m}+\frac{\Phi^{r}_{m}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))}{\Re{(\mathbf{K})}_{mm}},
\end{IEEEeqnarray}
 The update of $\tilde{\lambda}^{new}_{m}$ is completed by clipping based on (\ref{KKT complementary5})
\begin{IEEEeqnarray}[\relax]{l}
\lambda^{new}_{m}=[\tilde{\lambda}^{new}_{m}]^{CR^{'}(\xi_{m})}_{-CR^{'}(\xi_{m})}
\label{clipped new dual variable}
\end{IEEEeqnarray}

>>>>

  We first introduce 1-D work set selection strategy in which single optimization variable whose update can maximize the gain of the sub dual objective function is chosen as the work set in each iteration. Define $\Lambda=[\lambda_{1}, \lambda_{2}, \ldots, \lambda_{N_{r}}]^{T}$, $\sigma_{i}=\lambda_{i}^{new}-\lambda_{i}$, $\Sigma=[\sigma_{1}, \sigma_{2}, \ldots, \sigma_{N_{r}}]^{T}$. In (\ref{subset optimization}), substitute $\mathbf{a}, \hat{\mathbf{a}}$ by $\Lambda$ and in (\ref{gain work set selection2}), substitute $\Delta$ by $\Sigma$. Let $\Lambda_{S}$ and $\Sigma_{S}$ denote the vector that consist of the components in $\Lambda$ and $\Sigma$ that belong to work set $S$, the sub dual objective function in (\ref{subset optimization}) and its gain (\ref{gain work set selection2}) can be rewritten as 
  \begin{equation}
\max_{\Lambda_{S}}\quad \theta_{S}^{r}=-\frac{1}{2}[\Lambda_{S}^{T}\Re{(\mathbf{K})}_{SS}\Lambda_{S}]+[\Re{(\mathbf{y}_{S}^{T})}-\Lambda_{N}^{T}\Re{(\mathbf{K})}_{NS}
]\Lambda_{S}-\epsilon<\mathbf{e}_{S}^{T}, |\Lambda_{S}|>,
\label{subset optimization lambda}
\end{equation}

\begin{IEEEeqnarray}[\relax]{l}
\bigtriangledown \theta_{S}^{r}=-\frac{1}{2}\Sigma^{T}_{S}\Re{(\mathbf{K})}_{SS}\Sigma_{S}+(\Phi^{r}_{S})^{T}\Sigma_{S}-\epsilon<\mathbf{e}^{T}_{S},|\Lambda^{new}_{S}|-|\Lambda_{S}|>,
\label{gain work set selection lambda}
\end{IEEEeqnarray} 
In 1-D solver, $|S|=1$, based on (\ref{subset optimization lambda}), the sub dual objective function corresponding to the $m$th optimization variable $\tilde{\lambda}^{new}_{m}$, $m=1,2,\ldots, N_{r}$ can be written as
\begin{IEEEeqnarray}[\relax]{l}
 \max_{\tilde{\lambda}^{new}_{m}}\quad \theta_{m}^{r}=-\frac{1}{2}(\tilde{\lambda}_{m}^{new})^{2}\Re{(\mathbf{K})}_{mm}
+[\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\Re{(\mathbf{K})}_{mj}\lambda_{j}]\tilde{\lambda}_{m}^{new}-\epsilon(|\tilde{\lambda}^{new}_{m}|),
 \label{optimization function 1-D}
 \end{IEEEeqnarray}
 where $\tilde{\lambda}^{new}_{m}$ is the update of $\lambda_{m}$.
 Based on the definition of $\Phi$ in (\ref{gain work set selection2}), $\Phi^{r}_{i}=\Re{(\mathbf{y}_{i})}-\sum_{j=1}^{N_{r}}\lambda^{r}_{j}\Re{(\mathbf{K})}_{ij}$, similarly, as to dual variable $\lambda^{i}_{i}$ in the imaginary channel, $\Phi_{i}^{i}=\Im(y_{i})-\sum_{j=1}^{N_{r}}\lambda^{i}_{j}\Re{(\mathbf{K})}_{ij}$. Thereafter, for sake of brevity, we use $\lambda_{i}$ instead of $\lambda_{i}^{r}$.
Take the partial derivative of $\theta_{m}^{r}$ respect to $\tilde{\lambda}^{new}_{m}$,  we have 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\frac{\partial \theta_{m}^{r}}{\partial \tilde{\lambda}^{new}_{m}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Re{(\mathbf{y}_{m})}-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re{(\mathbf{K})}_{mj}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))
\label{partial optimization function 1-D lambda}
\end{IEEEeqnarray} 
where $\Re(y_{m})-\sum_{j\neq m}^{N_{r}}\lambda_{j}\Re(\mathbf{K})_{mj}=\Re(y_{m})-\sum_{j=1}^{N_{r}}\lambda_{j}\Re(\mathbf{K}_{mj})=\Phi^{r}_{m}+\lambda_{m}\Re(\mathbf{K}_{mm})$
and $\lambda_{m}$ denotes the $m$th optimization variable before update. Therefore (\ref{partial optimization function 1-D lambda}) can be rewritten as 
\begin{IEEEeqnarray}[\relax]{l}
\frac{\partial \theta^{r}_{m}}{\partial \tilde{\lambda}_{m}^{new}}=-\tilde{\lambda}_{m}^{new}\Re{(\mathbf{K})}_{mm}+\Phi^{r}_{m}+\lambda_{m}\Re{(\mathbf{K})}_{mm}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))\\
\Rightarrow \tilde{\lambda}_{m}^{new}=\lambda_{m}+\frac{\Phi^{r}_{m}-\epsilon(sgn(\tilde{\lambda}^{new}_{m}))}{\Re{(\mathbf{K})}_{mm}},
\end{IEEEeqnarray}
 The update of $\tilde{\lambda}^{new}_{m}$ is completed by clipping based on (\ref{KKT complementary5})
\begin{IEEEeqnarray}[\relax]{l}
\lambda^{new}_{m}=[\tilde{\lambda}^{new}_{m}]^{CR^{'}(\xi_{m})}_{-CR^{'}(\xi_{m})}
\label{clipped new dual variable}
\end{IEEEeqnarray}
